---
title: "Corporate Analysis"
author: "Vijayvithal"
date: "2 December 2015"
output: html_document
---

```{r setup ,include=FALSE}

require(knitr)
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
opts_knit$set(root.dir = normalizePath('../'))

# Libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(lubridate)
library(xtable)
library(scales)
library(readxl)
library(XML)

# Indian numeric quantities
lakh<-100000
crore<-10000000

#Edit this template at C:\Users\vsjahagi\Documents\RStudio\resources\templates
```

```{r}
files<-list.files("RawData/mca.gov.in/",full.names = T,pattern="*.xlsx")

library(RCurl)
curl = getCurlHandle()
agent="Mozilla/5.0" #or whatever

curlSetOpt(cookiejar="cookies.txt",  useragent = agent, proxy="proxy-iind.intel.com",proxyport=911,followlocation = TRUE, curl=curl)
#curlSetOpt(cookiejar="cookies.txt",  useragent = agent, followlocation = TRUE, curl=curl)
html=getURL( "http://www.mca.gov.in/DCAPortalWeb/dca/MyMCALogin.do?method=setDefaultProperty&mode=31",curl=curl)

getdin<-function(din){
  print (paste0("Din=",din))
  url=paste0("http://www.mca.gov.in/DCAPortalWeb/dca/SignatoryDetailsAction.do?method=viewSignatoryComp&cin=",din)
  html1<-getURL(url,curl=curl)
  if(grepl("table",html1)){
    if(grepl("Your Session has expired.",html1))
    {
      html=getURL( "http://www.mca.gov.in/DCAPortalWeb/dca/MyMCALogin.do?method=setDefaultProperty&mode=31",curl=curl)
      html1<-getURL(url,curl=curl)
      
    }
    tbl<-readHTMLTable(html1,as.data.frame=T,which=1,header=T,skip.rows = 1)
    if(!is.null(tbl) ){
      tbl%>%mutate(cin=din)
    }
  } else {
    print(paste0("Unable to find table for cin=",din))
    html=getURL( "http://www.mca.gov.in/DCAPortalWeb/dca/MyMCALogin.do?method=setDefaultProperty&mode=31",curl=curl)
  }
}
for (file in files){
kar<-read_excel(file)
kar$` PAIDUP_CAPITAL `<-extract_numeric(kar$` PAIDUP_CAPITAL `)
kar$REGISTERED_STATE<-as.factor(kar$REGISTERED_STATE)
kar$COMPANY_STATUS<-as.factor(kar$COMPANY_STATUS)
kar$COMPANY_CLASS<-as.factor(kar$COMPANY_CLASS)
kar$COMPANY_CATEGORY<-as.factor(kar$COMPANY_CATEGORY)
kar$REGISTRAR_OF_COMPANIES<-as.factor(kar$REGISTRAR_OF_COMPANIES)
kar$SUB_CATEGORY<-as.factor(kar$SUB_CATEGORY)
kar$PRINCIPAL_BUSINESS_ACTIVITY<-as.factor(kar$PRINCIPAL_BUSINESS_ACTIVITY)

html=getURL( "http://www.mca.gov.in/DCAPortalWeb/dca/MyMCALogin.do?method=setDefaultProperty&mode=31",curl=curl)
Sys.sleep(6)
state<-kar$REGISTERED_STATE[1]
print(paste0("State is ",state))
state<-gsub(" ","",state)
writefile<-paste0(state,"-directors.csv")
if(!file.exists(writefile)){
  cin_list=kar$CORPORATE_IDENTIFICATION_NUMBER;
  iterations=ceiling(length(cin_list)/1000)
  for(iter in 1:iterations){
    writefileiter<-paste0(state,iter,"-directors.csv")
    if(!file.exists(writefileiter)){
      
      start_iter<-1+(iter-1)*1000
      end_iter<-iter*1000
      datam<-na.omit(cin_list[start_iter:end_iter])
  #   directors<-lapply(datam,getdin)
      print(paste0("Finished subset of the directors for ",state,"iteration ",iter, " of ",iterations))
   #   dframe<-do.call(rbind,directors)
    #  write.csv(dframe,writefileiter)
    }
  }
    mframe=data.frame()
  for(iter in 1:iterations){
  #//TODO merge individual tables
        writefileiter<-paste0(state,iter,"-directors.csv")
        x<-read.csv(writefileiter)
    mframe<-rbind(mframe,x)
  }
  write.csv(mframe,writefile)

}
}
```
# Introduction
Ministry of corporate affairs puts out certain data related to corporate houses on its website, Is it possible to do a bulk analysis of the data to narrow down companies of interest?

* Can we identify "Gadkari Companies"? i.e. Potential Shell Companies whose directors stay far away (in a different state)
* Can we track the industralisation of India?
* Can we identify the rise and fall of different sectors?

## Data Sources
The data used for this analysis were downloaded from http://www.mca.gov.in/MinistryV2/masterdatareport.html on 2nd Dec 2015

## Data quality overview
# Overview of Analysis
#Results
#Appendix