---
title: "Crime against Women 2001-12"
author: "Vijayvithal"
date: "19 October 2015"
output: html_document
---

```{r setup ,include=FALSE,message=FALSE}

require(knitr)
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
opts_knit$set(root.dir = normalizePath('../'))

# Libraries
library(dplyr)
library(tidyr)
library(ggplot2)
```

# Analysis of National Crime records from 2001 to 2012.

Source: https://data.gov.in/resources/persons-arrested-under-crime-against-women-during-2001-2012/download 

To understand the defination of these crimes please refer to https://www.childlineindia.org.in/CP-CR-Downloads/Indian%20penal%20code%201860.pdf

e.g.

*354. Assault or criminal force to woman with intent to outrage her modesty*
—

Whoever assaults or uses criminal force to any woman, intending to outrage or
knowing it to be likely that he will thereby outrage her modesty, shall be punished
with imprisonment of either description for a term which may extend to two years,
or with fine, or with both.

*509. Word, gesture or act intended to insult the modesty of a woman —*

Whoever, intending to insult the modesty of any woman, utters any word, makes
any sound or gesture, or exhibits any object, intending that such word or sound
shall be heard, or that such gesture or object shall be seen, by such woman, or
intrudes upon the privacy of such woman, shall be punished with simple
imprisonment for a term which may extend to one year, or with fine, or with both. 

```{r}
caw<-read.csv("RawData/data.gov.in/pacCAW2001-12.csv")
library(tidyr)
caw_tidy<-gather(caw,Year,Count,X2001:X2012)
caw_total<-caw_tidy%>%filter(grepl("TOTAL",CRIME.HEAD))
caw_india<-caw_total%>%filter(grepl("STATES",STATE.UT))
ggplot(caw_india,aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~CRIME.HEAD )

```
The total crime against women across india is increasing year on year.

## Spread of crime across categories
Crime by category shows cruelty of husband is being reported more frequently. Also incidents of kidnapping have doubled. Most of the crimes are by a close relative (dowry death, harrassment by husband inlaws etc.)
```{r}
caw_india_total<-caw_tidy%>%filter(!grepl("TOTAL",CRIME.HEAD)) %>% filter(!grepl("STATES",STATE.UT))
ggplot(caw_india_total,aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~CRIME.HEAD )
```

# Statewise crime statistics

Karnataka has very less crime reporting compared to other states.

```{r}
caw_total%>%
  filter(!grepl("TOTAL",STATE.UT)) %>%
ggplot(aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~STATE.UT )
```

# Karnataka crime statistics

```{r}
caw_karnataka<-caw_tidy[grepl ("KARNATAKA",caw_tidy$STATE.UT),]
caw_karnataka<-caw_karnataka[!grepl ("TOTAL",caw_karnataka$CRIME.HEAD),]
ggplot(caw_karnataka,aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~CRIME.HEAD )

```

# Analysis of district wise data.

```{r}
caw<-read.csv("RawData/data.gov.in/dstrCAW_1.csv")
library(tidyr)
caw_tidy  <-gather(caw,Crime,Count,Rape:Importation.of.Girls)
caw_tidy <-caw_tidy%>%filter(!grepl("TOTAL",DISTRICT))
caw_karnataka <-caw_tidy%>%filter(grepl("KARNATAKA",STATE.UT))
ggplot(caw_karnataka,aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~DISTRICT )

caw_Bangalore <-caw_karnataka%>%filter(grepl("BANGALORE C",DISTRICT))
ggplot(caw_Bangalore,aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~Crime )
```

# What does the data say?
* Most of the crime registered are for domestic abuse.
* Over the past one decade we have not been able to make any impact on dowry death.
* A Domestic abuse case is normally a pre-cursor to a civil case (e.g. divorce proceedings). Is there a corelation between a disproportionate amount of domestic abuse case and civic cases? Shouldnt we be seeing more of eve-teasing cases("INSULT TO MODEST")
* Relative to national average, Karnataka had a higher number of cases under "immoral traffic act" which has decreased in recent years.
* The district wise dataset does not capture all the fields that are captured in the state wise dataset
* Almost every female has a story of eve-teasing(Insult to modesty) or groping(Assult on women with intent to ...) Why is it not being reported? What can be done to increase the legitimate reporting of such crimes?

# Prison Data
```{r}
prison<-read.csv("RawData/data.gov.in/Educational_standard_of_inmates.csv")
```
