---
title: "Crime against Women 2001-12"
author: "Vijayvithal"
date: "19 October 2015"
output: pdf_document
---

```{r setup ,include=FALSE,message=FALSE}

require(knitr)
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
opts_knit$set(root.dir = normalizePath('../'))

# Libraries
library(dplyr)
library(tidyr)
library(ggplot2)
```

# Analysis of National Crime records from 2001 to 2012.

Source: https://data.gov.in/resources/persons-arrested-under-crime-against-women-during-2001-2012/download 

```{r}
caw<-read.csv("RawData/data.gov.in/pacCAW2001-12.csv")
library(tidyr)
caw_tidy<-gather(caw,Year,Count,X2001:X2012)
caw_total<-caw_tidy%>%filter(grepl("TOTAL",CRIME.HEAD))
caw_india<-caw_total%>%filter(grepl("STATES",STATE.UT))
ggplot(caw_india,aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~CRIME.HEAD )

```
The total crime against women across india is increasing year on year.

## Spread of crime across categories
Crime by category shows cruelty of husband is being reported more frequently. Also incidents of kidnapping have doubled. Most of the crimes are by a close relative (dowry death, harrassment by husband inlaws etc.)
```{r}
caw_india_total<-caw_tidy%>%filter(!grepl("TOTAL",CRIME.HEAD)) %>% filter(!grepl("STATES",STATE.UT))
ggplot(caw_india_total,aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~CRIME.HEAD )
```

# Statewise crime statistics

Karnataka has very less crime reporting compared to other states.

```{r}
caw_total%>%
  filter(!grepl("TOTAL",STATE.UT)) %>%
ggplot(aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~STATE.UT )
```

# Karnataka crime statistics

```{r}
caw_karnataka<-caw_tidy[grepl ("KARNATAKA",caw_tidy$STATE.UT),]
caw_karnataka<-caw_karnataka[!grepl ("TOTAL",caw_karnataka$CRIME.HEAD),]
ggplot(caw_karnataka,aes(x=Year,y=Count))+geom_bar(stat="identity",position="dodge") +facet_wrap( ~CRIME.HEAD )

```
