---
title: "Data Processing"
author: "Vijayvithal"
date: "13 September 2015"
output: html_document
---

The data set for voters record is obtained from http://smartvote.in. This data is Collected everytime the CEO updates the voter list. Typicaly the data is scrapped via the reports published by the CEO to collect the following parameters.

Each set of data contains records of approximately 70 lakh voters. Loading and analyzing each of the dataset overloads the tool so as a first step we will break down the dataset into managable chunks.

```{r test-perl, engine='perl'}
use strict;
use warnings;
use Archive::Zip;
my $zip = Archive::Zip->new;
chdir "..";
exit(0) if(-d "csvfiles"); # This is a lengthy process, skip it if the script has been run before.

#########################################
#### Read the AC Number Mapping data
#########################################
open (FILE,"<RawData/AC_Name_No_Ward_mapping.txt") or die "unable to open AC-AC number mapping table for reading";
my %ac;
while (<FILE>){
  my ($ac,$no,@others) =split /\t/;
  $ac=~s/\s/_/g;
  $ac{$no}=$ac;
}
close(FILE);
mkdir "csvfiles";
my @files=glob("RawData/sv_data/*.zip");
my $prevfile="ViJaY";
foreach my $file(@files){
  my $outfile;
  $file=~/.*\/([^\/]*).zip/;
  my $dirname="csvfiles/".$1;
  next if(-e $dirname);
  mkdir $dirname;
  $zip->read ($file);
  foreach my $member ($zip->members){
    next if $member->isDirectory;
  $member->extractToFileNamed("Archive.csv");
  open(FILE,"<Archive.csv") or die " Unable to open extracted Archive.csv for reading";
  while (<FILE>){
    # Clean the data to remove punctuation marks which mess with the file reader.
    s/,/./g; # Remove comma's from source file
    s/^\s*//; # Remove Leading Spaces
    #s/"//g; # Remove Quotation marks like "
    #s/'/-/g; # catch single quote marks like D'souza
    s/\t-\t/\tNA\t/g; # Replace null entries with NA
    next if (/^\s*$/);
    my @fields=split("\t");
    $fields[0]=~/^[A-Za-z]*(...)/i;
    my $ACno=$1;
    my$ACname=$ac{$ACno};
    if($prevfile ne $ACname) {
      open (OFILE,">$dirname/$ACname.csv") or die "Unable to open file $dirname/$ACname.csv:$1 with $fields[0] fields @fields";
      $prevfile=$ACname;
    }
    print OFILE $_;
    
  }
  close(FILE);
  }
}
# By this point we have a folder called csvfiles which has a folder for each dataset further divided by AC's
```

As our next step we will analyze each data set and create age specific tables containing the following data.

Part | Age | Gender | Maritial Status | Count
-----|--|--|--|--
Part | Age | M/F | Married/Unknown | 0-9

This data will be stored in the "part_age_gender" folder in csv format.

We will also create a year level table summarising at the AC level instead of the part level

```{r testing}
print ("Testing")
```


```{r function}
#########################
## Function to read data for an AC, Clean the data return it.
#########################
read_ac<-function (filename) {
    file_path<-strsplit(filename,"/")[[1]]
  ac<-read.delim2(filename,header=F,quote="")
    headers<-read.delim2(paste(c(file_path[1:length(file_path)-1],"format.txt"),sep="/",collapse = '/'))
    colnames(ac)<-colnames(headers)
  # Remove incomplete entries
  ac<-ac[complete.cases(ac),]
  # Remove all entries showing incorrect Age
  ac$Age<-as.numeric(ac$Age)
  ac<-ac[ac$Age>=18 & ac$Age <=110,]
  return(ac)
}
```

```{r parse_data}
library(dplyr)
library(tidyr)
setwd("..")
if(FALSE){
ac_table<-data.frame(AC.Part=factor(),Age=numeric(),Gender=factor(),Maritial=factor(),Count=numeric())
prev_year<-"";
files<-list.files("csvfiles",recursive=T,full.names = T,pattern = "*.csv$")
if(!dir.exists("ac_part_age_gender")){
  dir.create("ac_part_age_gender")
}
  for (file in files) {
    print (file)
    file_path<-strsplit(file,"/")[[1]]
    year<-file_path[2]
    ac_name<-strsplit(file_path[3],".",fixed = T)[[1]][1]
    #if(file.exists(paste("part_age_gender",year,ac_name,collapse='/',sep="/"))){next}
    if(!file.exists(file)){
      print(paste0("File does not exist",file,"\n")) 
      next
      }
    ac<-read_ac(file)

#     if(year!=prev_year & prev_year!=""){
#       write.csv(ac_table,file=paste("ac_part_age_gender",prev_year,".csv",collapse='/',sep="/"))
#       prev_year<-year
#       ac_table<-data.frame(AC=factor(),Gender=factor(),Maritial=factor(),Age=numeric(),count=numeric())
#     }
    
    #####################################
    ### Part wise stats
    ####################################
    
    ac_d<-tbl_df(ac) %>%
      group_by(AC.Part,Age,Gender) %>%
      summarise(Married=sum(Rel=="H"),Unknown=n()-Married) %>%
      gather(key=Maritial,value= Count, -Age,-AC.Part,-Gender) %>%
      filter(Count!=0)
    dir.create(paste("part_age_gender",year,collapse='/',sep="/"),recursive = T)
    write.csv(ac_d,file=paste("part_age_gender",year,ac_name,collapse='/',sep="/"))
    
    #####################################
    ### AC wise stats
    ####################################

    ac_d<-tbl_df(ac) %>%
      group_by(Age,Gender) %>%
      summarise(Married=sum(Rel=="H"),Unknown=n()-Married) %>%
      gather(key=Maritial,value= Count, -Age,-Gender) %>%
      filter(Count!=0)%>%
      mutate(AC=ac_name, list=year) %>%
    ac_table<-rbind(ac_table,ac_d)
  }
    dir.create(paste("ac_part_age_gender",collapse='/',sep="/"),recursive = T)
    
      write.csv(ac_table,"ac_part_age_gender/Combined.csv")
      }
```
```{r}
setwd("..")
      #We messedup Yearly table creation in the previous set. let us retry :(
      files<- list.files("part_age_gender",recursive = T,full.names = T)
ac_table<-data.frame(AC=factor(),DataSet=factor(),Age=numeric(),Gender=factor(),Maritial=factor(),Count=numeric())
      for(file in files) {
            file_path<-strsplit(file,"/")[[1]]
    year<-file_path[1]
    ac_name<-file_path[2]
        
        ac<-read.csv(file)
        ac_cons<-tbl_df(ac) %>%
          group_by(Age,Gender,Maritial) %>%
          summarise(Count=sum(Count)) %>%
          mutate(AC=ac_name,DataSet=year)
        
       ac_table<- rbind(ac_table,ac_cons)
      }
    dir.create(paste("ac_part_age_gender",collapse='/',sep="/"),recursive = T)

      write.csv(ac_table,"ac_part_age_gender/Combined.csv")

      
      
```

Let us plot a few gender plots to ensure everything went ok.
```{r genderPlots}
library(ggplot2)
      ggplot(ac_table,aes(x=Age,y=Count))+geom_point()
      ggplot(ac_table,aes(x=Age,y=Count,color=Gender))+geom_point()
      ggplot(ac_table,aes(x=Age,y=Count,color=Gender))+geom_point()
#ggplot(x=)
```