---
title: "MP Salary"
author: "Vijayvithal"
date: "30 September 2015"
output: html_document
---

```{r setup ,include=FALSE}

require(knitr)
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
opts_knit$set(root.dir = normalizePath('../'))

# Libraries
library(dplyr)
library(tidyr)
library(ggplot2)
```
The press release for "formation of the committee on MP Salary" quotes certain data to imply that our MP's are under paid compared to their counter part's in the world.
While they claim to have survyed 37 countries around the world, the data presented by PRS contains only the top  "developed countries" and looks like this.
```{r}
sal<-read.csv("RawData/MP Salary.csv") %>%
  mutate(Citizen_Income=extract_numeric(PPP),MP_Income=Annual.Dollor,MP_Citizen_Ratio=X)
ggplot(sal,aes(x=Country,y=MP_Income)) +geom_bar(stat="identity")
```
While this figure makes our indian MP cut a poor figure in front of his global counterparts, The picture is not accurate, Let us also plot the average Salary of the citizen along with the MP.
```{r}
sal%>%gather(Income,Amount,MP_Income,Citizen_Income)%>% ggplot(aes(x=Country,y=Amount,fill=Income)) +geom_bar(stat="identity",position="dodge")
```

```{r}

  ggplot(sal,aes(x=Country,y=MP_Citizen_Ratio)) +geom_bar(stat="identity")

```
