---
title: "Understanding our parliament: word analysis of Rajyasabha sessions from 1952 to 2014"
author: "Vijayvithal"
date: "30 October 2015"
output: html_document
---

#Intorduction

The RS Data from 1952 to 2014 collected by http://www.lostprogrammer.com/blog/open-legislature/ Is used for this analysis. We are using the csv file available at https://drive.google.com/file/d/0B1RcWLku0ZOWdHcwZEhnX1hYS28/view?usp=sharing

While the RS has its own set of rollong appointments and does not coincide with the LS. We will use the same set of LS Durations to analyse the RS Data.

```{r setup ,include=FALSE}
require(knitr)
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
opts_knit$set(root.dir = normalizePath('../'))

# Libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(tm)
library(dplyr)
library(lubridate)
library(tidyr)
library(wordcloud)
library(RTextTools)
```


```{r cache=TRUE, readNclean}
a<-read.csv("RawData/datameet/debs.csv",header=F)
b<-separate(a,V3,c("dd","mm","yy"),sep="-")
b$yy<-extract_numeric(b$yy)
b<-mutate(b,yy=ifelse(yy>15 &yy<100,1900+yy,2000+yy))
b<-b[complete.cases(b),]
```


```{r message=FALSE}
start<-c(1952,1957,1962,1967,1971,1977,1980,1984,1989,1991,1996,1998,1999,2004,2009,2014)
end<-c(1957,1962,1967,1971,1977,1980,1984,1989,1991,1996,1998,1999,2004,2009,2014,2019)
ls_session<-cbind(start,end)

wordplot<-function(year,titles) {
 #str(titles) 
 #str(year)
today<-titles[titles$yy>=year[['start']] & titles$yy<year[['end']],]
x<-as.character(today$V6)
x<-strsplit(x," ")
x<-unlist(x)
x<-paste0(x,collapse = " ")
df1 <- data.frame(id=1:5, words=x)
matrix <- create_matrix(df1, stemWords=TRUE, removeStopwords=T, minWordLength=4)
m<-as.matrix(matrix)
word.freq <- sort(colSums(m), decreasing = T)
words<-data.frame(words=names(word.freq),freq=word.freq)
words<-words%>%top_n(100)
pal <- brewer.pal(9, "BuGn")
pal <- pal[-(1:4)]
#print(year)
wordcloud(words = words$words, freq = words$freq, min.freq = 3,
random.order = F, colors = pal)
return(nrow(today))
}

#We will be plotting the graph for the following years
print (ls_session)
#apply(ls_session,1,wordplot,titles=b)
```
The primary function of lawmakers is to make law. We would expect law making terms like bill, amendment, law, etc. to be the most frequently used term in their discussions

# First loksabha
The First loksabha session was from `r ls_session[1,][['start']]` to `r ls_session[1,][['end']]`
```{r}
num_q<-wordplot(ls_session[1,],titles=b)
```
During this time in RS A total of `r num_q` questions were raised
# Second loksabha
The Second loksabha session was from `r ls_session[2,][['start']]` to `r ls_session[2,][['end']]`
```{r}
num_q<-wordplot(ls_session[2,],titles=b)
```

* Delhi makes its appearence as the most frequently used word, For decades the state capital would be the most discussed word in the parliament.
* Bills have now moved off the primary list amendments and reports are now being discussed more frequently

# Third loksabha 

The third loksabha session was from `r ls_session[3,][['start']]` to `r ls_session[3,][['end']]`
```{r}
num_q<-wordplot(ls_session[3,],titles=b)
```

Now amendments and bills have moved off the priority list. It is all about reports now.

# 4th Loksabha

The fourth loksabha session was from `r ls_session[4,][['start']]` to `r ls_session[4,][['end']]`
```{r}
num_q<-wordplot(ls_session[4,],titles=b)
```

* India and Indian have now moved off the popularity list.
* Delhi and reports now occupy the discussions

#5th Loksabha

The fifth loksabha session was from `r ls_session[5,][['start']]` to `r ls_session[5,][['end']]`
```{r}
num_q<-wordplot(ls_session[5,],titles=b)
```

* Delhi and Reports are still firmly entrenched.

#6th Loksabha

The sixth loksabha session was from `r ls_session[6,][['start']]` to `r ls_session[6,][['end']]`

```{r}
num_q<-wordplot(ls_session[6,],titles=b)
```

* Delhi is now the center of discussion, india, report, banks are on the secondary list.
* Railway for some reason is not a popular discussion item in this session.

#7th Loksabha

The seventh loksabha session was from `r ls_session[7,][['start']]` to `r ls_session[7,][['end']]`

```{r}
num_q<-wordplot(ls_session[7,],titles=b)
```
* `r num_q` questains were raised in the Rajsabha during this period
* The dawn of liberalisation,
*india, occupies centerstage along with delhi and reports, develpoment, project, product are entering the vocabulary

#8th Loksabha

The eighth loksabha session was from `r ls_session[8,][['start']]` to `r ls_session[8,][['end']]`

```{r}
num_q<-wordplot(ls_session[8,],titles=b)
```

* `r num_q` questains were raised in the Rajsabha during this period
* Pradesh and reports occupy the center stage.

#9th Loksabha
The nineth loksabha session was from `r ls_session[9,][['start']]` to `r ls_session[9,][['end']]`

```{r}
num_q<-wordplot(ls_session[9,],titles=b)
```

* `r num_q` questains were raised in the Rajsabha during this period
* The first Atal government.
* This shortlived government saw reports back at the center stage.


#10 th Loksabha

The tenth loksabha session was from `r ls_session[10,][['start']]` to `r ls_session[10,][['end']]`
```{r}
num_q<-wordplot(ls_session[10,],titles=b)
```

* `r num_q` questains were raised in the Rajsabha during this period
* This government gave us the India shining campaign, but in their discussions India, and Indian were not the center point. neither were bills and amendments prominent in discussion. The discussion now centered on the business terms project, scheme, account, report, develop


#11th loksabha government

The eleventh loksabha session was from `r ls_session[11,][['start']]` to `r ls_session[11,][['end']]`
```{r}
num_q<-wordplot(ls_session[11,],titles=b)
```

* `r num_q` questains were raised in the Rajsabha during this period
* Reports are back at the center.

#12 LS

The twelveth loksabha session was from `r ls_session[12,][['start']]` to `r ls_session[12,][['end']]`
```{r}
num_q<-wordplot(ls_session[12,],titles=b)
```

* `r num_q` questains were raised in the Rajsabha during this period
* Railways are back from their long exile as one of the main discussion points.
* Interest in the nation reawakens
* India has now started "Demanding"
* Projects reports develop are still going strong.

# 13 LS

The thirteenth loksabha session was from `r ls_session[13,][['start']]` to `r ls_session[13,][['end']]`
```{r}
num_q<-wordplot(ls_session[13,],titles=b)
```

# 14 LS

The 14th loksabha session was from `r ls_session[14,][['start']]` to `r ls_session[14,][['end']]`
```{r}
num_q<-wordplot(ls_session[14,],titles=b)
```

# 15 LS

The 15th loksabha session was from `r ls_session[15,][['start']]` to `r ls_session[15,][['end']]`
```{r}
num_q<-wordplot(ls_session[15,],titles=b)
```

# 16 LS

The 16th loksabha session was from `r ls_session[16,][['start']]` to `r ls_session[16,][['end']]`
```{r}
num_q<-wordplot(ls_session[16,],titles=b)
```
