---
title: "Toll Analysis"
author: "Vijayvithal"
date: "3 November 2015"
output: html_document
---

```{r setup ,include=FALSE}

require(knitr)
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
opts_knit$set(root.dir = normalizePath('../'))
options(digits=4,scipen = 9)

# Libraries
library(scales)
library(dplyr)
library(tidyr)
library(ggplot2)
library(RCurl)
library(XML)
library(xml2)
library(lubridate)
library(xtable)
if(file.exists("RawData/toll.tgz")) {
untar("RawData/toll.tgz",compressed="gzip",exdir="RawData/tolldata")
}
lakh<-100000
crore<-10000000
```

```{r functions,cache=T}
read_fees<-function(filename,index,booth_name,booth_index=1){
   fees_df <-
      readHTMLTable(
        filename,header = T,which = index,as.data.frame = T
      ) 
   
    if(!is.null(fees_df)) {
     if (dim(fees_df)[2] == 4) {
    fees_df <-
      mutate(fees_df,"Commercial Vehicle Registered within the district of plaza " =
               NA)
  }
      fees_df<-mutate(fees_df,tollbooth = booth_name,route=booth_index)
    }
   return(fees_df)
}

##################################
#Initialize Structures
##################################

# Fees to be paid at booth.
fees<-data.frame("Type of vehicle"=factor(),
                 "Single Journey"=numeric(),
                 
                 "Return Journey"=numeric(),
                 "Monthly Pass"=numeric(),
                 "Commercial Vehicle Registered within the district of plaza "=numeric(),
                 tollbooth=character())


# Cost of road construction
cost<-data.frame();

# Facilities on Road
facilities<-data.frame();

# Booth location and other metadata.
booth<-data.frame();


for (filename in list.files("RawData/tolldata/data/",full.names = T,pattern =
                            "Toll")) {
  #print (filename)
  x <- read_html(filename)
  
  # XPATH PArsing to get unstructured data.
  
  booth_name <- xml_text(xml_find_all(x,"//lable"))
  concession <-
    xml_text(xml_find_all(x,'//*[@id="Messages"]/div/div[2]/div[1]/ul/li'))
  concession <- ifelse(length(concession) != 0,concession,NA)
  fee_dates <- xml_text(xml_find_all(x,'//*[@id="Messages"]/div/p[2]'))
  location <- xml_text(xml_find_one(x,'//*[@id="Messages"]/div/p[1]'))
  
  fees_df<-read_fees(filename,1,booth_name,1)
  fees <- rbind(fees,fees_df)
  
  cost_df <-
    readHTMLTable(
      filename,header = F,which = 2,as.data.frame = T
    ) %>%
    mutate(tollbooth = booth_name)
  cost <- rbind(cost,cost_df)
# Some booths have multiple destination based fees Capturing all the fee information
  if (length(readHTMLTable(filename)) == 7) {
  fees_df<-read_fees(filename,3,booth_name,2)
  if(!is.null(fees_df)){
    fees <- rbind(fees,fees_df)
  }
    facilities_df <-
      readHTMLTable(
        filename,header = F,which = 4,as.data.frame = T
      ) %>% mutate(tollbooth = booth_name)
    
  }else if (length(readHTMLTable(filename)) == 8) {
  fees_df<-read_fees(filename,3,booth_name,2)
  if(!is.null(fees_df)){
    fees <- rbind(fees,fees_df)
  }
  fees_df<-read_fees(filename,4,booth_name,3)
  if(!is.null(fees_df)){
    fees <- rbind(fees,fees_df)
    }
    facilities_df <-
      readHTMLTable(
        filename,header = F,which = 5,as.data.frame = T
      ) %>% mutate(tollbooth = booth_name)
  } else{
    facilities_df <-
      readHTMLTable(
        filename,header = F,which = 3,as.data.frame = T
      ) %>% mutate(tollbooth = booth_name)
    
  }
  booth_df <-
    data.frame(
      tollbooth = booth_name,concession = concession,fee_dates = fee_dates,location =
        location,check.rows = F
    )
  
  facilities <- rbind(facilities,facilities_df)
  booth <- rbind(booth,booth_df)
  
}
```

```{r TidyData}
##############################################################
########  Tidy up the Data
##############################################################

booth_tidy<-booth%>%
  separate(fee_dates,c("Effective.Date","Revision.Due.Date"),sep="/") %>%
mutate(Effective.Date=dmy(Effective.Date),
       Revision.Due.Date=dmy(Revision.Due.Date))%>%
  separate(location,c("location","Road.Length"),sep="Tollable Length :")%>%
  separate(location,c("location","Stretch"),sep="Stretch :")%>%
  separate(Road.Length,c("Min.Road.Length","Max.Road.Length"),sep="to|/|&|[(]") %>%
  mutate(Min.Road.Length=extract_numeric(Min.Road.Length))
aa<-regexpr("[(][^)]*[)] *$",booth_tidy$tollbooth,perl=T)
booth_tidy<-mutate(booth_tidy,funding.Model=regmatches(booth_tidy$tollbooth,aa))

  

fees_tidy<-fees[complete.cases(fees$`Type of vehicle`),] %>%
  rename(Type.of.vehicle=`Type of vehicle`,
         Single.Journey=`Single Journey`,
         Return.Journey=`Return Journey`,
         Monthly.Pass=`Monthly Pass`,
         Local.Commercial.Vehicle=`Commercial Vehicle Registered within the district of plaza `
         )%>%
  filter(route==1)%>%
  mutate(Single.Journey=extract_numeric(Single.Journey),
         Return.Journey=extract_numeric(Return.Journey),
         Monthly.Pass=extract_numeric(Monthly.Pass),
         Local.Commercial.Vehicle=extract_numeric(Local.Commercial.Vehicle))
  
cost_tidy<-cost%>%spread(V1,V2)%>%
  separate(`Target Traffic (PCU/day)`,c("Target.Traffic","Target.Date"),sep=" As on :")%>%
  separate(`Traffic (PCU/day)`,c("Actual.Traffic","Actual.Date"),sep="As on :")%>%
  separate(`Date of fee notification`,c("Fee.Notification.Date","Fee.Notification.No"),sep="[(]") %>%
  separate(`Commulative Toll Revenue (in Rs. Cr.)`,c("Cumulative.Revenue","Cumulative.Date"),sep="As on :")%>%
  mutate(Cumulative.Revenue.Discounted=grepl("With Discounting",Cumulative.Revenue))

##################################################
cost_tidy<-cost_tidy%>%
  mutate(`Capital Cost of Project (in Rs. Cr.)`=extract_numeric(`Capital Cost of Project (in Rs. Cr.)`),
         `Capital Cost of Project (in Rs. Cr.)`=ifelse(`Capital Cost of Project (in Rs. Cr.)`/crore>=1,`Capital Cost of Project (in Rs. Cr.)`,crore*`Capital Cost of Project (in Rs. Cr.)`) , # It looks like some entries are in rupees instead of crores. Fixing those.
         `Commercial Operation Date`=dmy(`Commercial Operation Date`),
         Cumulative.Date=dmy(Cumulative.Date),
         Fee.Notification.Date=dmy(Fee.Notification.Date),
         `Design Capacity (PCU)`=extract_numeric(`Design Capacity (PCU)`),
         Target.Traffic=extract_numeric(Target.Traffic),
         Target.Date=dmy(Target.Date),
         Actual.Traffic=extract_numeric(Actual.Traffic),
         Actual.Date=dmy(Actual.Date)) %>%
           rename(
             Capital.cost=`Capital Cost of Project (in Rs. Cr.)`,
             Commercial.Operation.Date=`Commercial Operation Date`,
             Design.Capacity=`Design Capacity (PCU)`,
             Incharge=`Name / Contact Details of Incharge`,
             Contractor=`Name of Concessionaire / OMT Contractor`
           
  )%>%
  mutate(
    Cumulative.Revenue=extract_numeric(Cumulative.Revenue),
    Cumulative.Revenue=ifelse(Cumulative.Revenue/crore>1,Cumulative.Revenue,
                              ifelse(Cumulative.Revenue/lakh>1,Cumulative.Revenue*100,Cumulative.Revenue*crore))
  )
         


joined<-left_join(fees_tidy,booth_tidy,by="tollbooth")
joined<-left_join(joined,cost_tidy)
write.table(joined,"TollData.data")
```
```{r DataInference}
#We take this joined Data and add some more datapoints to it
joined<-joined%>%
  mutate(recovery=Capital.cost/(365*Actual.Traffic*Single.Journey))%>%
  mutate(cost.per.km=Capital.cost/Min.Road.Length)%>%
  filter(route==1) # In case of multiple routes at a toll plaza we will take only one route in consideration.
cars<-filter(joined,grepl("Car",Type.of.vehicle))
cpkm<-cars
cpkm<-cpkm[!is.infinite(cpkm$cost.per.km),]
cpkm<-cpkm[!is.na(cpkm$cost.per.km),]
```

```{r SummaryReport}
cuml_rev<-cost_tidy$Cumulative.Revenue
earning2date<-sum(cuml_rev[complete.cases(cuml_rev)])

n<-top_n(cost_tidy,1,desc(Commercial.Operation.Date))
earliest.operation<-n$Commercial.Operation.Date
earliest.revenue<- n$Cumulative.Revenue
earliest.toll<-n$tollbooth
earliest.capital=n$Capital.cost

m<-top_n(cost_tidy,1,desc(Actual.Traffic))
recovery_period<-cars%>%
  select(tollbooth,Single.Journey,Actual.Traffic,Capital.cost,funding.Model,Commercial.Operation.Date)
recovery_period<-recovery_period[complete.cases(recovery_period),]%>%
  mutate(recovery=Capital.cost/(365*Actual.Traffic*Single.Journey),Commercial.Operation.Date=as.character(Commercial.Operation.Date))



```

# Introduction

## Data sources

This is an analysis of the toll information available at http://www.nhtis.org/tolllist.htm

The RawData, processed data and the scripts used to generate this report are available on github at github.com/jahagirdar/Data-Driven-Policy/tollBooth.Rmd

The data from the website was downloaded on 3rd November 2015 and saved as HTML for each tollbooth. This report is based on the saved html files.

This data can be accessed on github as RawData/toll.tgz

## Issues with the data.
The downloaded data has the following reliability issues.

* The revenue column is in crores, Data for some of the booths runs in Crores of Crores, We assume that the data was not entered in Crores and fix for the same.  
 * Similarly some of the revenue data is in Lakhs of crores and is assumed to be incorrect data entry and fixed for the same.
* Some toll booths show abnormally high daily traffic running in tens of lakhs to multiple crores. We are not sure what is wrong with these booths and have left them as is.

## Overview

* In India, on most of the highways we see toll booth's spaced at a distance of approximate an hours drive time or less.
* These toll roads are build under one of the following models.
```{r results="asis"}
x<-cpkm%>% group_by(funding.Model)%>%
summarize(Number.Of.Booth=n(),
'Median Cost/km in Crores'=median(na.omit(cost.per.km))/crore, 'Total Cost in Crores'=sum(na.omit(Capital.cost))/crore,'Total Length in km'=sum(na.omit(Min.Road.Length))
) %>%
arrange(desc(Number.Of.Booth))
print( xtable(x , caption="Funding model of toll roads(Note: toll booths with incomplete information are ignored in this table)"),type="html")
```
```{r results="asis"}
ggplot(cpkm,aes(cost.per.km))+geom_histogram()+facet_wrap(~funding.Model)+ylab("Number of Toll roads")
ggplot(joined,aes(funding.Model,cost.per.km))+geom_boxplot()
```

* BOT:Build Operate Transfer
* OMT: (Operate Maintain Transfer(?))

* Most of the public funded toll roads were constructed at a lower cost/km  
* Median cpkm of public funded roads is `r median(na.omit(cpkm%>%filter(funding.Model=="( Public Funded ) ")%>%select(cost.per.km))$cost.per.km)/crore` Crores.
* Median cpkm of roads built under BOT is `r median(na.omit(cpkm%>%filter(funding.Model=="( BOT ) ")%>%select(cost.per.km))$cost.per.km)/crore` Crores.

i.e. a Road built under BOT model is twice as costly as a road built under Public funding model.


* The earliest still operating tollbooth is at `r earliest.toll` which was built at a capital cost of  `r earliest.capital/crore` crores and started commercial operation in `r earliest.operation`
* After that, toll building started taking off in the 2000's with the maximum number of toll booths commissioned during the UPA-2 government. Most of the toll roads under BOT and Public funding models were built during this period.

* Today we have `r nrow(booth_tidy)` Toll locations across India. These toll booths were constructed at a cost of `r sum(cost_tidy$Capital.cost,na.rm=T)/(lakh * crore)` Lakh Crores. The cost of `r sum(is.na(cost_tidy$Capital.cost))` toll booths is not known.

```{r}
ggplot(cars,aes(Commercial.Operation.Date,fill=funding.Model))+geom_histogram()+xlab("Start of Commercial Operation") +ylab("Number of Booths")+facet_wrap(~funding.Model)
```

* The total declared earnings since commercial operation from these toll booths is `r round(earning2date/(crore * lakh))` lakh Crores.
* `r sum(na.omit(cars$Actual.Traffic))/lakh` lakh vehicles use these toll booths daily.
* `r 365*sum(na.omit(cars$Actual.Traffic*cars$Single.Journey))/(lakh*crore)` Lakh Crore Is the total amount that should be earned this year based on actual average daily traffic. i.e. On averge cost recovery for the toll road takes place within `r sum(na.omit(cost_tidy$Capital.cost))/(365*sum(na.omit(cars$Actual.Traffic* cars$Single.Journey)))` years.
* At this rate the total investment in all toll roads should be recovered in `r (sum(na.omit(cost_tidy$Capital.cost),na.rm=T) -earning2date)/ (365*sum(na.omit(cars$Actual.Traffic*cars$Single.Journey)))`  years.

* If we drop the top 10% of the booths seeing heavy traffic and re calculate the above numbers we get the following:
```{r}
bot_90<-cars%>%filter(Actual.Traffic<=quantile(cars$Actual.Traffic,na.rm=T,probs=1:10/10)[9])
```
* `r sum(na.omit(bot_90$Actual.Traffic))/lakh` lakh vehicles use these toll booths daily.
* `r 365*sum(na.omit(bot_90$Actual.Traffic*bot_90$Single.Journey))/(lakh*crore)` Lakh Crore Is the total amount that should be earned this year based on actual average daily traffic. i.e. On averge cost recovery for the toll road takes place within `r sum(na.omit(bot_90$Capital.cost))/(365*sum(na.omit(bot_90$Actual.Traffic* bot_90$Single.Journey)))` years.
* At this rate the total investment in all toll roads should be recovered in `r (sum(na.omit(bot_90$Capital.cost),na.rm=T) -earning2date)/ (365*sum(na.omit(bot_90$Actual.Traffic*bot_90$Single.Journey)))`  years.

* Some roads see very heavy traffic while some roads makes you wonder why were they built? e.g.

# Low Daily traffic


```{r results="asis"}
print(xtable(top_n(cost_tidy,5,desc(Actual.Traffic))%>%mutate(Capital.cost.Crore=Capital.cost/crore,Cumulative.Revenue.Crore=Cumulative.Revenue/crore,Commercial.Operation.Date=as.character(Commercial.Operation.Date)) %>%select(tollbooth,Actual.Traffic,Design.Capacity,Capital.cost.Crore,Cumulative.Revenue.Crore,Commercial.Operation.Date)%>%arrange((Actual.Traffic)),caption="The 5 toll roads seeing the least traffic."),type="html")
```

It is not clear how a toll booth seeing less than 100 vehicles a day i.e. less than 36 thousand vehicles a year or approx a lakh vehicle since it commenced operation collected a revenue of 27 Crores or 2700 per vehicle per day per trip. 

#High Daily Traffic

On the other hand some of the toll booths seeing heavy traffic have already paid off the investment or are half way through.
The number for average daily traffic look fishy. It is difficult to imaging a tollbooth seeing average daily traffic running in tens of lakhs or crores.

Toll boths measuring traffic of over a lakh vehicle daily are:
```{r results="asis"}
x<-cost_tidy%>%
     mutate(Capital.cost.Crore=Capital.cost/crore,Cumulative.Revenue.Crore=Cumulative.Revenue/crore,Commercial.Operation.Date=as.character(Commercial.Operation.Date))%>%
    select(tollbooth,Actual.Traffic,Design.Capacity,Capital.cost.Crore,Cumulative.Revenue.Crore,Commercial.Operation.Date)%>%
    filter(Actual.Traffic>lakh)%>%
    arrange(desc(Actual.Traffic))
  
print(xtable(x ,caption="The  toll roads seeing the most traffic."),type="html")
```




# Investment recovery period.
```{r results="asis"}
   x<- cars%>%filter(Cumulative.Revenue>=Capital.cost)%>%mutate(Capital.Cost.Crore=Capital.cost/crore,Revenue=Cumulative.Revenue/crore, Commercial.Operation.Date=as.character(Commercial.Operation.Date))%>%
select(tollbooth,Capital.Cost.Crore,Revenue,Commercial.Operation.Date)
```

In theory toll booths seeing heavy traffic should have repaid the capital cost within a few years of operation. Data indicates `r nrow(x)` toll roads have reached this milestone.
```{r results="asis"} 

print(
  xtable(x  ,caption="Toll booths which have already paid back the investment"),type="html")
```

Based on the current average daily traffic, The cost recovery period for toll booths is as follows
```{r results="asis"}
print(xtable(recovery_period%>%mutate(Capital.cost=Capital.cost/crore)%>%rename(Capital.cost.in.Crores=Capital.cost)%>%arrange((recovery))%>%rename(recovery.in.years=recovery)),type="html")
ggplot(cpkm,aes(cost.per.km,fill=funding.Model))+geom_histogram(position="dodge")+facet_wrap(~funding.Model)+ylab("Number of Toll roads")
ggplot(recovery_period,aes(recovery))+geom_histogram(binwidth=5)+coord_cartesian(xlim=c(0,100))+xlab("Cost recovery in years")+  scale_x_continuous(breaks=pretty_breaks(n=10)) +ylab("Number of booth")

#+coord_cartesian(xlim=c(0,100))
```

# Appendix

```{r plotGraphs}
ggplot(cost_tidy,aes(Capital.cost/crore))+geom_histogram()+xlab("Capital cost of project in crore")+ylab("Number of Booths")
ggplot(cost_tidy,aes(Actual.Traffic))+geom_histogram(binwidth=5000)+coord_cartesian(xlim=c(0,100000))+ylab("Number of Booths") +xlab("Average Daily Traffic")
```

```{r}
ggplot(cpkm,aes(cost.per.km/crore))+geom_histogram() +ylab("Number of Booths") +xlab("Cost per km (Crores") +  scale_x_continuous(breaks=pretty_breaks(n=30)) +ylab("Number of booth")
lmfit<-coef(lm(Commercial.Operation.Date ~ cost.per.km,cpkm))
ggplot(cpkm,aes(x=Commercial.Operation.Date,y=cost.per.km))+geom_point()+geom_smooth()
#abline(intercept=lmfit[[1]],slope=lmfit[[2]])
```

# Note

* `r sum(cost_tidy$Cumulative.Revenue.Discounted)` Booth Have some revenue discounting scheme. We are not sure what these schemes are.
* we have an outlier where the cost/km is over 250 Crores this corresponds to 

```{r results="asis"}
print(xtable(select(top_n(cpkm,1,cost.per.km),tollbooth,cost.per.km,Min.Road.Length,location,Actual.Traffic,Capital.cost)),type="html")
```
