---
title: "Toll Analysis"
author: "Vijayvithal"
date: "3 November 2015"
output: html_document
---

```{r setup ,include=FALSE}

require(knitr)
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
opts_knit$set(root.dir = normalizePath('../'))
options(digits=4,scipen = 9)

# Libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(RCurl)
library(XML)
library(xml2)
library(lubridate)
library(xtable)
if(file.exists("RawData/toll.tgz")) {
untar("RawData/toll.tgz",compressed="gzip",exdir="RawData/tolldata")
}
lakh<-100000
crore<-10000000
```

```{r functions,cache=T}
read_fees<-function(filename,index,booth_name,booth_index=1){
   fees_df <-
      readHTMLTable(
        filename,header = T,which = index,as.data.frame = T
      ) 
   
    if(!is.null(fees_df)) {
     if (dim(fees_df)[2] == 4) {
    fees_df <-
      mutate(fees_df,"Commercial Vehicle Registered within the district of plaza " =
               NA)
  }
      fees_df<-mutate(fees_df,tollbooth = booth_name,route=booth_index)
    }
   return(fees_df)
}

##################################
#Initialize Structures
##################################

# Fees to be paid at booth.
fees<-data.frame("Type of vehicle"=factor(),
                 "Single Journey"=numeric(),
                 
                 "Return Journey"=numeric(),
                 "Monthly Pass"=numeric(),
                 "Commercial Vehicle Registered within the district of plaza "=numeric(),
                 tollbooth=character())


# Cost of road construction
cost<-data.frame();

# Facilities on Road
facilities<-data.frame();

# Booth location and other metadata.
booth<-data.frame();


for (filename in list.files("RawData/tolldata/data/",full.names = T,pattern =
                            "Toll")) {
  #print (filename)
  x <- read_html(filename)
  
  # XPATH PArsing to get unstructured data.
  
  booth_name <- xml_text(xml_find_all(x,"//lable"))
  concession <-
    xml_text(xml_find_all(x,'//*[@id="Messages"]/div/div[2]/div[1]/ul/li'))
  concession <- ifelse(length(concession) != 0,concession,NA)
  fee_dates <- xml_text(xml_find_all(x,'//*[@id="Messages"]/div/p[2]'))
  location <- xml_text(xml_find_one(x,'//*[@id="Messages"]/div/p[1]'))
  
  fees_df<-read_fees(filename,1,booth_name,1)
  fees <- rbind(fees,fees_df)
  
  cost_df <-
    readHTMLTable(
      filename,header = F,which = 2,as.data.frame = T
    ) %>%
    mutate(tollbooth = booth_name)
  cost <- rbind(cost,cost_df)
# Some booths have multiple destination based fees Capturing all the fee information
  if (length(readHTMLTable(filename)) == 7) {
  fees_df<-read_fees(filename,3,booth_name,2)
  if(!is.null(fees_df)){
    fees <- rbind(fees,fees_df)
  }
    facilities_df <-
      readHTMLTable(
        filename,header = F,which = 4,as.data.frame = T
      ) %>% mutate(tollbooth = booth_name)
    
  }else if (length(readHTMLTable(filename)) == 8) {
  fees_df<-read_fees(filename,3,booth_name,2)
  if(!is.null(fees_df)){
    fees <- rbind(fees,fees_df)
  }
  fees_df<-read_fees(filename,4,booth_name,3)
  if(!is.null(fees_df)){
    fees <- rbind(fees,fees_df)
    }
    facilities_df <-
      readHTMLTable(
        filename,header = F,which = 5,as.data.frame = T
      ) %>% mutate(tollbooth = booth_name)
  } else{
    facilities_df <-
      readHTMLTable(
        filename,header = F,which = 3,as.data.frame = T
      ) %>% mutate(tollbooth = booth_name)
    
  }
  booth_df <-
    data.frame(
      tollbooth = booth_name,concession = concession,fee_dates = fee_dates,location =
        location,check.rows = F
    )
  
  facilities <- rbind(facilities,facilities_df)
  booth <- rbind(booth,booth_df)
  
}
```

```{r TidyData}
booth_tidy<-booth%>%
  separate(fee_dates,c("Effective.Date","Revision.Due.Date"),sep="/") %>%
mutate(Effective.Date=dmy(Effective.Date),
       Revision.Due.Date=dmy(Revision.Due.Date))%>%
  separate(location,c("location","Road.Length"),sep="Tollable Length :")%>%
  separate(location,c("location","Stretch"),sep="Stretch :")%>%
  separate(Road.Length,c("Min.Road.Length","Max.Road.Length"),sep="to|/|&|[(]") %>%
  mutate(Min.Road.Length=extract_numeric(Min.Road.Length))

fees_tidy<-fees[complete.cases(fees$`Type of vehicle`),] %>%
  rename(Type.of.vehicle=`Type of vehicle`,
         Single.Journey=`Single Journey`,
         Return.Journey=`Return Journey`,
         Monthly.Pass=`Monthly Pass`,
         Local.Commercial.Vehicle=`Commercial Vehicle Registered within the district of plaza `
         )%>%
  mutate(Single.Journey=extract_numeric(Single.Journey),
         Return.Journey=extract_numeric(Return.Journey),
         Monthly.Pass=extract_numeric(Monthly.Pass),
         Local.Commercial.Vehicle=extract_numeric(Local.Commercial.Vehicle))
  
cost_tidy<-cost%>%spread(V1,V2)%>%
  separate(`Target Traffic (PCU/day)`,c("Target.Traffic","Target.Date"),sep=" As on :")%>%
  separate(`Traffic (PCU/day)`,c("Actual.Traffic","Actual.Date"),sep="As on :")%>%
  separate(`Date of fee notification`,c("Fee.Notification.Date","Fee.Notification.No"),sep="[(]") %>%
  separate(`Commulative Toll Revenue (in Rs. Cr.)`,c("Cumulative.Revenue","Cumulative.Date"),sep="As on :")%>%
  mutate(Cumulative.Revenue.Discounted=grepl("With Discounting",Cumulative.Revenue))

##################################################
cost_tidy<-cost_tidy%>%
  mutate(`Capital Cost of Project (in Rs. Cr.)`=crore*extract_numeric(`Capital Cost of Project (in Rs. Cr.)`),
         `Commercial Operation Date`=dmy(`Commercial Operation Date`),
         Cumulative.Date=dmy(Cumulative.Date),
         Fee.Notification.Date=dmy(Fee.Notification.Date),
         `Design Capacity (PCU)`=extract_numeric(`Design Capacity (PCU)`),
         Target.Traffic=extract_numeric(Target.Traffic),
         Target.Date=dmy(Target.Date),
         Actual.Traffic=extract_numeric(Actual.Traffic),
         Actual.Date=dmy(Actual.Date)) %>%
           rename(
             Capital.cost=`Capital Cost of Project (in Rs. Cr.)`,
             Commercial.Operation.Date=`Commercial Operation Date`,
             Design.Capacity=`Design Capacity (PCU)`,
             Incharge=`Name / Contact Details of Incharge`,
             Contractor=`Name of Concessionaire / OMT Contractor`
           
  )%>%
  mutate(
    Cumulative.Revenue=crore*extract_numeric(Cumulative.Revenue)
  )
         


joined<-left_join(fees_tidy,booth_tidy,by="tollbooth")
joined<-left_join(joined,cost_tidy)
cars<-filter(joined,grepl("Car",Type.of.vehicle))
```

```{r SummaryReport}
cuml_rev<-cost_tidy$Cumulative.Revenue
earning2date<-sum(cuml_rev[complete.cases(cuml_rev)])

n<-top_n(cost_tidy,1,desc(Commercial.Operation.Date))
earliest.operation<-n$Commercial.Operation.Date
earliest.revenue<- n$Cumulative.Revenue
earliest.toll<-n$tollbooth
earliest.capital=n$Capital.cost

m<-top_n(cost_tidy,1,desc(Actual.Traffic))
recovery_period<-cars%>%
  select(tollbooth,Single.Journey,Actual.Traffic,Capital.cost)
recovery_period<-recovery_period[complete.cases(recovery_period),]%>%
  mutate(recovery=Capital.cost/(365*Actual.Traffic*Single.Journey))
ggplot(recovery_period,aes(recovery))+geom_histogram(binwidth=5)+coord_cartesian(xlim=c(0,100))


x<-select(cars,Single.Journey ,Actual.Traffic)
x<-x[complete.cases(x),]
```

# Introduction

In India, on most of the highways we see toll booth's spaced at a distance of approximate an hours drive time or less. The data related to these toll booths

* `r nrow(booth_tidy)` Toll locations across India.
* `r sum(cost_tidy$Capital.cost,na.rm=T)/(lakh * crore)` Lakh Crore was spent on the toll roads bridges etc.
* `r round(earning2date/(crore * lakh))` lakh Crores was cumulatively earned from all toll booths since they were constructed.
* `r sum(x$Actual.Traffic)` Vehicles use these toll booths daily.
* `r 365*sum(x$Actual.Traffic*x$Single.Journey)/(lakh*crore)` Lakh Crore Is the total amount that should be earned this year based on Actual average daily traffic and min fees(for Car)
* `r sum(cost_tidy$Cumulative.Revenue.Discounted)` Booth Have some revenue discounting scheme.
* `r earliest.toll` is the Earliest toll booth which commenced operation in `r  earliest.operation` and is still collecting revenue. It has collected a revenue of `r earliest.revenue/(lakh*crore)` lakh Crores for a capital investment of  `r earliest.capital/crore` Crore
* The least busiest toll booth is `r m$tollbooth` with `r m$Actual.Traffic` vehicles per day. costing `r m$Capital.cost`

```{r plotGraphs}
ggplot(cost_tidy,aes(Capital.cost))+geom_histogram()+xlab("Capital cost of project")+ylab("Number of Booths")
ggplot(cost_tidy,aes(Commercial.Operation.Date))+geom_histogram()+xlab("Start of Commercial Operation") +ylab("Number of Booths")
ggplot(cost_tidy,aes(Actual.Traffic))+geom_histogram(binwidth=5000)+coord_cartesian(xlim=c(0,100000))+ylab("Number of Booths") +xlab("Average Daily Traffic")
```

```{r}
cpkm<-left_join(cost_tidy,booth_tidy,by="tollbooth")%>% mutate(cost.per.km=Capital.cost/Min.Road.Length)
ggplot(cpkm,aes(cost.per.km))+geom_histogram()
```
we have an outlier where the cost/km is over 250 Crores this corresponds to 
```{r results="asis"}
cpkm<-cpkm[!is.infinite(cpkm$cost.per.km),]
print(xtable(select(top_n(cpkm,1,cost.per.km),tollbooth,cost.per.km,Min.Road.Length,location,Actual.Traffic,Capital.cost)),type="html")
```

At the current Average traffic and assuming all vehicles are cars(lowest fees) Toll booths should recover their investment within

```{r results="asis"}
print(xtable(recovery_period%>%mutate(Capital.cost=Capital.cost/crore)%>%rename(Capital.cost.in.Crores=Capital.cost)%>%arrange((recovery))),type="html")
```